\section{Problems and Issues}
\begin{itemize}
	\item Getting in sync with stakeholders
	\item Frontend development
\end{itemize}

\subsection{Getting in sync with stakeholders}
The success of this project relies on convincing you two that it
could work. The issue that I am having is that I cannot develop all the frontends
myself that will show a complete user experience.

Currently my priorities are:
\begin{itemize} 
	\item Backend: Make the tactical algorithm dynamic and functioning respect constraints 
	\item Frontend: Let you manually upload resources
	\item Frontend: Let you see live updating of the currect resource profile of the schedule 
		that the algorithm is generating.
\end{itemize}

So questions for you if you disagree with the priorities:
\begin{itemize}
	\item \colorbox{yellow}{\textbf{What aspects of the program does each of you think should be prioritized now?}}
	\item \colorbox{yellow}{\textbf{I believe that making this program work without any involvement of a offshore}}	\\
    	\colorbox{yellow}{\textbf{supervisor (the person responsible for assigning names to the technicians) }} \\
		\colorbox{yellow}{\textbf{will be very difficult. Do you aggee or disagree?}}
\end{itemize} 

\subsection{Frontend Development}
My background is in solving scheduling problems, and it is 
my judgement that the kind of scheduling problem that we are facing cannot be solved
without the user interactions from the \textbf{Scheduler}, \textbf{Supervisor} 
and the \textbf{Technician} (we will skip them for now). That means that I cannot 
simply rely on my skills in coding scheduling systems, we need frontends to provide 
you (and supervisors) with the \textbf{schedules} that the system generates so that 
each scheduler (and supervisor) and quickly iterate on the schedules. 
