
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Christian\\Brunbjerg\\Jespersen}}}} % First name
	
	\vspace{6pt}
	
	{\Large Engineer $\sim$ Mathematician} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	\icon{Globe}{11}{\href{http://www.google.com}{\parbox{2cm}{github.com/\\scipo-code}}}\\ 
    \icon{Phone}{11}{0045 2843 3974}\\
    \icon{MapMarker}{11}{\parbox{2cm}{Copenhagen\\Denmark}}\\
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\icon{Envelope}{11}{\href{mailto:chri1423@gmail.com}{chri1423@gmail.com}}\\	
    \icon{Github}{11}{\href{https://github.com/uma-dev}{github.com/brunbjerg}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com}{in/cbrje}}\\    
\end{minipage}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}

 	Technically skilled operation researcher, confident in metaheuristic design, implementation, and deployment.

	Able to manage a project including scoping, data collection, interviewing, and stakeholder management.

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
	  All programming languages
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
    	Linux, Docker, Kubernetes, PKI, Nix.
    \end{minipage}
    
\end{minipage}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
		{Technology}
		{Scheduling System API}
		{github.com/scipo-code/ordinator-api.git}
		{
        	Main repository for the backend API of my Ph.D. project.
		}
	\entry
		{Technology}
		{Matheuristics in Maintenance Scheduling}
		{github.com/brunbjerg/MaintenanceSchedulingMatheuristic.git}
		{ 
			Large Neighborhood Search based matheuristics for the maintenance scheduling problem.
		}
    \entry
		{Technology}
		{Optimization of Fuel Delivery}
		{github.com/brunbjerg/optimization-of-fuel-delivery.git}
		{ 
			Master thesis project. 
		}
    \entry
		{Technology}
		{Poker Stochastic Probability Simulator}
		{
			github.com/brunbjerg/probker.git
		}
		{ 
			Hobby project \\ 
			Frontend: github.com/brunbjerg/probker-frontend.git
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
	\entry
		{2/2023 - 2/2026}
		{Ph.D. in Multi-actor Maintenance Scheduling}
		{Total Energies, DTU Construct, and DTU Management}
		{
			Multi-threaded Scheduling Systems, API development, Interviewing, Testing with Stakeholders. 
		}
    \entry
		{9/2020 - 12/2022}
		{Master in Mathematical Modelling and Computation - Operation Research }
		{DTU Compute}
		{
			Metaheuristics, Statistics, Programming. 
		}
    \entry
		{9/2017 - 7/2020}
		{Bachelor in Mathematical Engineering - Operation Research}
		{DTU Compute}
		{
			Algorithms, Operation Research.
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {2017 -- 2022}
		{Teaching Assistant}
		{Technical University of Denmark}
		{
			\vspace{-10pt}
	        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
	            \item Mathematical Programming Modelling 
	            \item Programming of Scientific Software
	        \end{itemize} 
	        \texttt{Teaching}
		}
	\entry
		{1/2010 -- 12/2020}
		{Production Operator and Maintenance Technician}
		{Nordic Sense}
		{
			\vspace{-10pt}\\
			I have worked for years at my familie's factory working with everything from \\
			production tasks to maintaining and commissioning new machines. This has \\ 
			proven to be a valuable experience throughout my current Ph.D. programme.\\
			\texttt{Ownership}
        }
	\entry
		{9/2016 -- 7/2017 \\\footnotesize{}}
		{Production Operator and Maintenance Technician}
		{Grundfos}
		{
			\vspace{-10pt}\\
	        Production technician for 4 months and Maintenance technician for 5 months\\
			\texttt{Practical Production} \slashsep \texttt{Practical Maintenance}
        }
	\entry
		{7/2015 -- 6/2016 \\\footnotesize{}}
		{Event promotor}
		{Det Blå Danmark}
		{
			\vspace{-10pt}\\
	    	Shows that I can step out of my introverted comfort zone when I need to. \\
	        \texttt{Event coordination}
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.46\textwidth}
	\cvsect{Languages}
    \vspace{-6pt}
    
	\begin{minipage}{0.28\textwidth}
    \textbf{English:} 
	\end{minipage}
	\hfill
	\begin{minipage}{0.65\textwidth}
		Fluent
	\end{minipage}

	\vspace{4mm}
	
	\begin{minipage}{0.28\textwidth}
		\textbf{Danish:}
	\end{minipage}
	\hfill
	\begin{minipage}{0.65\textwidth}
		Native
	\end{minipage}

	\vspace{4mm}
	
	\begin{minipage}{0.28\textwidth}
		\textbf{French:}
	\end{minipage}
	\hfill
	\begin{minipage}{0.65\textwidth}
		Want to learn
	\end{minipage}
\end{minipage}
\hfill
\begin{minipage}[t]{0.465\textwidth}
	\cvsect{Blindspots}
    \vspace{-6pt}

	\begin{minipage}[t]{0.28\textwidth}
		\textbf{Communication:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.65\textwidth}
		Introverted. Tends towards solitary work. Prefer fewer but close work partners.
	\end{minipage}

	\vspace{4mm}

	\begin{minipage}[t]{0.28\textwidth}
		\textbf{Consistency:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.65\textwidth}
		Strategic thinker with focus on vision. Beneficial to be part of a team on important milestones.
	\end{minipage}

\end{minipage}

%----------------------------------------------------------------------------------------
\end{document}
